Estimating duration in the presence of misclassification

### 2024-07-29 transmission.tex
Rob typo comments

A slow increase in incidence is estimated to occur over the autumn 2020 period, peaking in October in most regions (see \cref{transmission:fig:backcalc-regions}).
An exception is the North East and East of England regions (see \cref{transmission:fig:backcalc-regions}(C) and (D) respectively); these regions show no consistent increase or decrease in incidence during October.
All regions then decrease during November; partially coincidng with the national lockdown in force in England between 5 Nov and 2 Dec 2020~\autocite{ifgTimeline}.

@@

The incidence proportion was highest among the 12--16 and 17--25 age groups throughout the period (see \cref{transmission:fig:backcalc-ages}).
Except the 17--25 age group, all age groups show similar trends (\ie parallel lines on a log scale), meaning there was insufficient information in the data to overcome the prior which favoured this situation.
The incidence proportion in the 17--25 age group decreases faster than other age groups during November.
There are many plausible explanations for this effect.
The higher incidence in this age group prior to November means it could be an immunity effect.
Alternatively, it could be a consequence of schools remaining open in the November lockdown; 20--24 year olds rarely interact with school-aged children (see \cref{E-SEIR:fig:age-contacts})
Further work is required to determine causality.
\begin{figure}
    \makebox[\textwidth][c]{\includegraphics[width=.9\paperwidth]{transmission/backcalc-ages}}
    \caption[Incidence estimated using the phenomenological approach by age group]{%
        Incidence proportion for each age group, on both natural and log scales.
    }
    \label{transmission:fig:backcalc-ages}
\end{figure}

@@

I take information on the contact rates, $\kappa_{aa'}(t)$, from several data sources, using the methodology of \textcite{vanleeuwenTime,vanleeuwenAugmenting}.
%; these estimates have been used for previous modelling of the SARS-CoV-2 pandemic~\autocite{vanleeuwenTime,birrellRealtime}.
% These start with estimates of contact in each setting, based on \textcite{vanleeuwenAugmenting}.
This method starts with pre-pandemic baseline estimates of $\kappa_{aa'}$ from the POLYMOD study~\autocite{mossongSocial}, and time use from the UKTUS (UK Time Use Survey)~\autocite{UKTUS}.
POLYMOD asked a representative sample of the UK population about the contacts they make each day, including information on each contact's age and location (home, work, school, leisure, transport, or other).
UKTUS asked a representative sample of the UK population about how much time they spent doing various activities (\eg shopping and spending time at home) each day.
\Textcite{vanleeuwenAugmenting} combined these two datasets to estimate the rate of contacts between age groups during each activity.
\Textcite{birrellRealtime} then modify these contact rates based on measured changes in time use during the pandemic.
These changes are measured using Google mobility data~\autocite{googleCOVID19} and school attendance data~(unpublished).
Google mobility data are based on the location of Android users over time, relative to a pre-pandemic baseline.
The mobility and school data are averaged over a week down or up-weight the number of contacts in each setting, before combining contacts across settings to form $\kappa_{aa'}(t)$.
$\kappa_{aa'}(t)$ is assumed to be piecewise constant, changing only at the start of each week.
For further details see \textcite{vanleeuwenAugmenting} and \textcite[supplementary material]{birrellRealtime}.

>>>>

A slow increase in incidence is estimated to occur over the autumn 2020 period, peaking in October in most regions (see \cref{transmission:fig:backcalc-regions}).
An exception is the North East and East of England regions (see \cref{transmission:fig:backcalc-regions}(B)); these regions show no consistent increase or decrease in incidence during October.
All regions then decrease during November; partially coinciding with the national lockdown in force in England between 5 Nov and 2 Dec 2020~\autocite{ifgTimeline}.

@@

The incidence proportion was highest among the 12--16 and 17--25 age groups throughout the period (see \cref{transmission:fig:backcalc-ages}).
Except the 17--25 age group, all age groups show similar trends (\ie parallel lines on a log scale), meaning there was insufficient information in the data to overcome the prior which favoured this situation.
The incidence proportion in the 17--25 age group decreases faster than other age groups during November.
There are many plausible explanations for this effect.
The higher incidence in this age group prior to November means it could be an immunity effect.
Alternatively, it could be a consequence of schools remaining open in the November lockdown; 20--24 year olds rarely interact with school-aged children (see \cref{E-SEIR:fig:age-contacts}).
Further work is required to determine causality.
\begin{figure}
    \makebox[\textwidth][c]{\includegraphics[width=.9\paperwidth]{transmission/backcalc-ages}}
    \caption[Incidence estimated using the phenomenological approach by age group]{%
        Incidence proportion for each age group, on both natural and log scales.
    }
    \label{transmission:fig:backcalc-ages}
\end{figure}

@@

I take information on the contact rates, $\kappa_{aa'}(t)$, from several data sources, using the methodology of \textcite{vanleeuwenTime,vanleeuwenAugmenting}.
%; these estimates have been used for previous modelling of the SARS-CoV-2 pandemic~\autocite{vanleeuwenTime,birrellRealtime}.
% These start with estimates of contact in each setting, based on \textcite{vanleeuwenAugmenting}.
This method starts with pre-pandemic baseline estimates of $\kappa_{aa'}$ from the POLYMOD study~\autocite{mossongSocial}, and time use from the UKTUS (UK Time Use Survey)~\autocite{UKTUS}.
POLYMOD asked a representative sample of the UK population about the contacts they make each day, including information on each contact's age and location (home, work, school, leisure, transport, or other).
UKTUS asked a representative sample of the UK population about how much time they spent doing various activities (\eg shopping and spending time at home) each day.
\Textcite{vanleeuwenAugmenting} combined these two datasets to estimate the rate of contacts between age groups during each activity.
\Textcite{birrellRealtime} then modify these contact rates based on measured changes in time use during the pandemic.
These changes are measured using Google mobility data~\autocite{googleCOVID19} and school attendance data~(unpublished).
Google mobility data are based on the location of Android users over time, relative to a pre-pandemic baseline.
The mobility and school data are averaged over a week, used to down or up-weight the number of contacts in each setting, and then combined across settings to form $\kappa_{aa'}(t)$.
$\kappa_{aa'}(t)$ is assumed to be piecewise constant, changing only at the start of each week.
For further details see \textcite{vanleeuwenAugmenting} and \textcite[supplementary material]{birrellRealtime}.
